---
title: "RRR: Wegner & Erber (1992) & Wegner et al., (1987)"
author: "Adam Wang, Martin Hagger, Kai Qin Chan, Ian Hussey"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

Contributions:

- R codes by Kai Qin Chan
- Test data by Kai Qin Chan
- Code refactoring and review by Ian Hussey, of the code version dated 18 Oct 2022

The below codes comprises two major segments:

1. R codes for analysis of single-lab data
2. R codes for meta analysis of multi-lab data

```{r include=FALSE}

# formatting options
# set default chunk options
knitr::opts_chunk$set(message = FALSE, 
                      warning = FALSE)

# disable scientific notation
options(scipen = 999) 

```

# Summary and critique of multilevel models

"Because the design has two within-subject factors (word type: target vs. nontarget words; time pressure: high vs. low), within a regression, this must be modeled as a MLM." - this isn't the case? But the fact that the data is being collected at multiple sites with the acknowledged potential for differences in scoring strategies between them is a reason to include site in the model. This would also align the multilevel models with the meta-analysis models (recognising that meta-analyses are a type of constrained multilevel model).

## Study 1

where:
- meancorrectresponse = \TODO - *why is the simulated data 0/1 for this? Is it just averaged between the scorers? Doesn't the manuscript say that differences will be resolved prior to analyses? If its binary data, shouldn't we use a logistic regression?*
- Cond = Express-first vs Suppress-first
- timepressure = \TODO short vs long time pressure to respond, operationalises cogntiive load. thought to be a moderator of the effect but not central to the claim that the effect is present in both, right?? Manipulated within subjects
- wordtype (target vs non-tartet). \TODO manipulated within. only wordtype=="target" relevant to testing the verbal hypothesis, right??
- Replication = target word type (e.g., food, disease, gorilla, tiger)

meancorrectresponse ~ 1 + Cond * timepressure * Replication + (1 | SubjID) + (1 | Replication)

meancorrectresponse ~ 1 + Cond * timepressure * wordtype + (1 | SubjID)

```{r eval=FALSE}

data_long_mod <- data_long_mod |>
  # use only word type == "target", ie target trials
  filter(wordtype == "target")

# fit negative binomial mixed-effects model
model <- lmer(meancorrectresponse ~ 1 + Cond + timepressure + (1 | site) + (1 | Replication), 
              data = data_long_mod)

```

- Cond & timepressure are not of direct interest to establishing the presence of the effect, they're just controlled for. Should they both therefore be effect coded (-.5, +.5)?
- Cond and timepressure entered as fixed main effects only, without an interaction, as the interaction seems poorly justified re mapping onto the verbal claim and throws off the effect coding. Marginal means could get around this ofc.  
- Assuming the above is correct, key effect to be scrutinized is the intercept. 
- Stimulus type (Replication) is smoothed over to make a general conclusion. Of course, this means including 'food' and 'disease', neither of which are "direct replications" of the original study and which introduce new unknowns. Ideally we'd stick to known categories, but then there's a trade off between using fewer than 4 levels to the random effect (bad) vs including sub ideal ones (also bad). On balance, use the data at hand, since the verbal claim is general too. You could scrutinise the random effect levels for Replication to see the variation here. 
- Same goes for variation between sites. Would be better to also do data control and check that consistent scoring was used, so that heterogeneity in the effect can be usefully attributed to participant sources rather than an unknown combination of method + participant sources.

## Study 2

Text from manuscript: "To replicate the rebound effect, each lab recruited a minimum post-exclusion sample of 80 participants to a study adopting a 2 (initial instructions: suppression vs. concentration) X 4 (target thought: gorilla vs. tiger vs. food vs. diseases; random intercept) between-participants experimental design, with target thought included as a random factor only for generalizability purposes, rather than as a central independent variable."
- This description does not map onto the code at all.

where:
- intrusions = (mean of two) counts
- Cond = Express-first vs Suppress-first
- Period = when participants got the instruction? "In the RRR, we only need the period 2 DV." - is period = 1 even collected then, and if so why?
- Replication = target word type (e.g., food, disease, gorilla, tiger)

intrusions ~ 1 + Cond * Period * Replication + (1 | SubjID)

intrusions ~ 1 + Cond * Replication + (1 | Replication) 
- Using the subset where Period == 2 

"Alternatively, if one assumes that Replication (targetwords) is not a variable of interest, then RUNIF:"
intrusions ~ 1 + Cond * Period + (1 | SubjID)

"RUNIF Replication is treated as a random effect (i.e., participants are nested within target word)"
intrusions ~ 1 + Cond * Period * Replication + (1 | Replication:SubjID)

Critiques

- The text in the manuscript does not map onto the models at all.
- All of the above are linear models despite 'intrusions' being count data. Negative binomial would be more appropriate
- low vs high cognitive load (time pressure) doesn't seem to be present in either the ANOVA or the MLM but only the meta??
- data collection site not included in the dataset for the individual labs or the multilevel model

Suggested appropriate model:

```{r eval=FALSE}

# dependencies
library(lme4)
library(MASS) 

data_long_mod <- data_long_mod |>
  # some method of making the intrusions counts between raters agree and be whole numbers would be needed (eg find agreement in all cases via discussion and rescoring). quick and dirty here:
  mutate(intrusions = ceiling(intrusions)) |>
  # use only the second period, based on above instructions and my partial understanding of the design from the description in the manuscript
  filter(period == 2)

# fit negative binomial mixed-effects model
model <- glmer.nb(intrusions ~ 1 + Cond + (1 | site) + (1 | Replication), 
                  data = data_long_mod)

```

- Cond is not of direct interest to establishing the presence of the effect, it's just controlled for. Should it therefore be effect coded (-.5, +.5)?
- Key effect to be scrutinized is the intercept. 
- Stimulus type (Replication) is smoothed over to make a general conclusion. Of course, this means including 'food' and 'disease', neither of which are "direct replications" of the original study and which introduce new unknowns. Ideally we'd stick to known categories, but then there's a trade off between using fewer than 4 levels to the random effect (bad) vs including sub ideal ones (also bad). On balance, use the data at hand, since the verbal claim is general too. You could scrutinise the random effect levels for Replication to see the variation here. 
- Same goes for variation between sites. Would be better to also do data control and check that consistent scoring was used, so that heterogeneity in the effect can be usefully attributed to participant sources rather than an unknown combination of method + participant sources.

## Meta-analysis

Unclear how they extract these summary stats (Ms, SD, and interaction effects) from individual sites, or why not just use multilevel models consistently to estimate this effect? 

Why split the time pressure if its just a moderator of the effect?

\TODO

# Dependencies

```{r}

library(readxl)
library(psych)
library(reshape2)
library(magrittr)
library(dplyr)
library(afex)
library(emmeans)
library(metafor)
library(forestplot)

```

# Data analysis for single labs

## For Wegner & Erber (1992)

### Import data

```{r}

RRR_WE92 <- read_excel("RRR_Hyperaccesibility.xlsx", sheet = "testdata_W&E'92_singlelab") #note: test data has hidden columns of RTs. RTs were not of interested in W&E'92 but may still be captured.
View(RRR_WE92)

RRR_metaWE92 <- read_excel("RRR_Hyperaccesibility.xlsx", sheet = "testdata_W&E'92_multilab")
View(RRR_metaWE92)

RRR_metaWegner87 <- read_excel("RRR_Hyperaccesibility.xlsx", sheet = "testdata_Wegner'87_multilab")
View(RRR_metaWegner87)

data_meta_1 <- read_excel("RRR_Hyperaccesibility.xlsx", sheet = "forestplot")
View(data_meta_1)

data_meta_2 <- read_excel("RRR_Hyperaccesibility.xlsx", sheet = "forestplotd1d2") #note new sheet name
View(data_meta_2)

```

### Data wrangling

```{r}

# Define categorical variables
RRR_WE92$Gender.participant <- factor(RRR_WE92$Gender.participant, levels = c("Male", "Female", "Other", "Prefer not to disclose"))
RRR_WE92$Gender.experimenter <- factor(RRR_WE92$Gender.experimenter, levels = c("Male", "Female", "Other", "Prefer not to disclose"))


# Convert wide format to long format
# This is needed for the mixed ANOVA analyses
data_long<-melt(RRR_WE92, id.vars=c("SubjID", "Cond", "Cond_num", "Replication", "targetword"), 
                measure.vars=c("mean.correctresponse.r1r2.target.low", "mean.correctresponse.r1r2.target.high", "mean.correctresponse.r1r2.nontarget.low", "mean.correctresponse.r1r2.nontarget.high"),
                variable.name="condition",
                value.name="meancorrectresponse") %>% arrange(SubjID)

# Create columns that define (split) the within-subject factors, i.e., time pressure and word type.
data_long$timepressure<-gl(2, 1, labels = c("Low", "High")) #define the factor and levels of the factor
data_long$wordtype<-gl(2, 2, labels = c("Target", "Nontarget")) #define the factor and levels of the factor

data_long$Cond<-factor(data_long$Cond,labels = c("Supression", "Concentration")) 
data_long$Cond_num<-factor(data_long$Cond_num,labels = c("Concentration", "Supression")) #note the swap
data_long$Replication<-factor(data_long$Replication,labels = c("1", "2", "3", "4")) 
data_long$timepressure<-factor(data_long$timepressure,labels = c("Low", "High")) 
data_long$wordtype<-factor(data_long$wordtype,labels = c("target", "nontarget")) 
data_long$SubjID<-factor(data_long$SubjID) #It doesn't seem to be necessary. Not sure.

```

### Manipulation check

To test whether the manipulation (concentration vs. suppression) produced different count outcomes in the manipulation check variable.

```{r}

chisq.test(RRR_WE92$Cond, RRR_WE92$Manipulationcheck, correct=FALSE)

```

### Intra-class correlation coefficients (correct responses only)

\TODO subsetting data by those who passed the manipulation check is commented as "##NOT RUN## (as specified by Editor)" but the code is not actually commented out- unclear if its to be run or not

subset data that passed manipulation checks. ##NOT RUN## (as specified by Editor)

```{r}

RRR_WE92 <- subset(RRR_WE92, Manipulationcheck=="1") #1 = passed manipulation checks.

```

```{r}

ICCdata1 <- data.frame(cbind(RRR_WE92$correctresponse.rater1.target.low1, RRR_WE92$correctresponse.rater2.target.low1))
ICC(ICCdata1)

ICCdata2 <- data.frame(cbind(RRR_WE92$correctresponse.rater1.target.high1, RRR_WE92$correctresponse.rater2.target.high1))
ICC(ICCdata2)

ICCdata3 <- data.frame(cbind(RRR_WE92$correctresponse.rater1.nontarget.low1, RRR_WE92$correctresponse.rater2.nontarget.low1))
ICC(ICCdata3)

ICCdata4 <- data.frame(cbind(RRR_WE92$correctresponse.rater1.nontarget.high1, RRR_WE92$correctresponse.rater2.nontarget.high1))
ICC(ICCdata4)

ICCdata5 <- data.frame(cbind(RRR_WE92$correctresponse.rater1.target.low2, RRR_WE92$correctresponse.rater2.target.low2))
ICC(ICCdata5)

ICCdata6 <- data.frame(cbind(RRR_WE92$correctresponse.rater1.target.high2, RRR_WE92$correctresponse.rater2.target.high2))
ICC(ICCdata6)

ICCdata7 <- data.frame(cbind(RRR_WE92$correctresponse.rater1.nontarget.low2, RRR_WE92$correctresponse.rater2.nontarget.low2))
ICC(ICCdata7)

ICCdata8 <- data.frame(cbind(RRR_WE92$correctresponse.rater1.nontarget.high2, RRR_WE92$correctresponse.rater2.nontarget.high2))
ICC(ICCdata8)

```

### Mixed ANOVA

```{r}

#Run 2 x 2 x 2 ANOVA (as reported by E&W 1992)
mainresult<-aov_ez(id = "SubjID", 
                   dv = "meancorrectresponse", 
                   between = "Cond", 
                   within = c("timepressure", "wordtype"),
                   data = data_long)

summary(mainresult)
emmeans(mainresult, pairwise ~ Cond|timepressure, adjust = "none") 
emmeans(mainresult, pairwise ~ timepressure|Cond, adjust = "none") 

#The results are expected to be significant only for the target words. 
#So, we need to restrict subsequent analyses to target words only.

#Remove rows with nontarget words, if needed
long2 <- data_long[!(data_long$wordtype=="nontarget"),]

#Rerun ANOVA, but now as a 2 x 2 ANOVA.
result2<-aov_ez(id = "SubjID", 
                dv = "meancorrectresponse", 
                between = "Cond", 
                within = c("timepressure"),
                data = long2)

summary(result2)
emmeans(result2, pairwise ~ Cond|timepressure, adjust = "none") 
emmeans(result2, pairwise ~ timepressure|Cond, adjust = "none") 

#Plot 2 x 2
emmip(result2, Cond~timepressure, xlab = "Condition", ylab = "Mean correct response", CIs = T) 

```

### Multilevel model

UPDATED: Jun 2022 (as requested by Editor)
This update specifies the four target words as random factor. Incidentally, the variable name for the four target words is called 'replication'. This word 'replication' is also used in the orignial Wegner & Erber article. Resource: For specifying the random effect, see ourcodingclub.github.io/tutorials/mixed-models/

```{r}

m1 <- lmer(formula = meancorrectresponse ~ 1 + Cond * timepressure * Replication + (1 | SubjID) + (1 | Replication), 
           data = long2) 
#Corrected in Oct 22: Participant is a random intercept; changed from glmer to lmer.
#Note also that the dataframe is long2 (nontarget words removed), not data_long.
summary(m1)

```

Update: Oct 2022 (as requested by Editor)
The following codes is meant to retrieve the beta and standard error of the three-way interaction (Cond x Time pressure x Word Type), so that a subsequent multi-lab meta-analysis of this three-way interaction term (which requires the point estimate and the variance) can be computed.
Because the design has two within-subject factors (word type: target vs. nontarget words; time pressure: high vs. low), within a regression, this must be modeled as a MLM. 
Condition (suppression vs. expression) is a between-subjects factor, hence this is not an issue.

```{r}

m2 <- lmer(formula = meancorrectresponse ~ 1 + Cond * timepressure * wordtype + (1 | SubjID), 
           data = data_long) #The factor, Replications, is omitted. It was not required by the Editor.
summary(m2)

```

## For Wegner et al. (1987)

### Import data

```{r}

RRR_Wegner87 <- read_excel("RRR_Hyperaccesibility.xlsx", sheet = "testdata_Wegner'87_singlelab")
View(RRR_Wegner87)

```

### Data wrangling

```{r}

#Define categorical variables
RRR_Wegner87$Gender.participant <- factor(RRR_Wegner87$Gender.participant, levels = c("Male", "Female", "Other", "Prefer not to disclose"))
RRR_Wegner87$Gender.experimenter <- factor(RRR_Wegner87$Gender.experimenter, levels = c("Male", "Female", "Other", "Prefer not to disclose"))


#Convert wide format to long format (RRR_Wegner87)
#This is needed for the MLM analyses. Note that this uses two DVs (period 1 and period 2). 
#In the RRR, we only need the period 2 DV.
# data_long<-melt(RRR_Wegner87, 
#                 id.vars=c("SubjID", "Cond", "Cond_num", "Replication", "targetword"), 
#                 measure.vars=c("finalDV.period1", "finalDV.period2"),
#                 variable.name="Period",
#                 value.name="intrusions") %>% 
#   arrange(SubjID)
# 
# #Define factors in the long format data.
# data_long$Cond<-factor(data_long$Cond,labels = c("Supression-first", "Concentration-first")) 
# data_long$Cond_num<-factor(data_long$Cond_num,labels = c("Concentration-first", "Supression-first")) #note the swap
# data_long$Period<-factor(data_long$Period,labels = c("1", "2"))
# data_long$Replication<-factor(data_long$Replication,labels = c("1", "2")) #Unlike RRR_WE92, there are only two replications for RRR_Wegner87. Note: replication is the same as targetword, except represented as numeric variable, instead of text.
# data_long$SubjID<-factor(data_long$SubjID) #It doesn't seem to be necessary. Not sure.

# Ian: I reworked the above into a tidyverse workflow to ensure i understood it.
library(forcats)
library(stringr)

data_long <- RRR_Wegner87 |>
  select(SubjID, Cond, Replication, targetword, period1 = finalDV.period1, period2 = finalDV.period2) |>
  pivot_longer(cols = c("period1", "period2"),
               values_to = "intrusions",
               names_to = "Period") |>
  mutate(Cond = dplyr::recode(Cond, 
                              "Suppress-first" = "Supression-first",
                              "Express-first" = "Concentration-first"),
         Cond = fct_relevel(Cond, "Supression-first", "Concentration-first"),
         Period = as.numeric(str_remove(Period, "period")),
         SubjID = as.factor(SubjID))

```

### Manipulation check

To test whether the manipulation (concentration vs. suppression) produced different count outcomes in the manipulation check variable.

Beware: No cell count should be < 5.

```{r}

chisq.test(RRR_Wegner87$Cond, RRR_Wegner87$Manipulationcheck, correct=FALSE)

```

### Intra-class correlation coefficients (for mentions only)

\TODO subsetting data by those who passed the manipulation check is commented as "##NOT RUN## (as specified by Editor)" but the code is not actually commented out- unclear if its to be run or not

Selecting data that passed manipulation checks. ##NOT RUN## (as specified by Editor)

```{r}

RRR_Wegner87 <- subset(RRR_Wegner87, Manipulationcheck=="1") #1 = passed manipulation checks.

```

```{r}

#Intra-class correlation coefficients 
ICCdata1 <- data.frame(cbind(RRR_Wegner87$totalmention.rater1.period1, RRR_Wegner87$totalmention.rater2.period1))
ICC(ICCdata1)

ICCdata2 <- data.frame(cbind(RRR_Wegner87$count.bellonly.rater1.period1, RRR_Wegner87$count.bellonly.rater2.period1))
ICC(ICCdata2)

ICCdata3 <- data.frame(cbind(RRR_Wegner87$count.mentiononly.rater1.period1, RRR_Wegner87$count.mentiononly.rater2.period1))
ICC(ICCdata3)

ICCdata4 <- data.frame(cbind(RRR_Wegner87$count.simulresponse.rater1.period1, RRR_Wegner87$count.simulresponse.rater2.period1))
ICC(ICCdata4)

```

### Mixed ANOVA

```{r}

#Main analyses
mainresult<-aov_ez(id = "SubjID", dv = "finalDV.period2", data=RRR_Wegner87, 
                   between = c("Cond", "targetword")) #note: As written in the RRR, "For the experiments testing the rebound effect, the dependent variable was the number of ‘food-related’ or ‘elephant-related’ thought occurrences during the second phase of the study where all participants were asked to express their thoughts freely."  That's why Period is not a within-subjects factor.

summary(mainresult)

#RUN IF interaction is significant and/or main effect of target word is found.
emmeans(mainresult, pairwise ~ Cond|targetword, adjust = "none") 
emmeans(mainresult, pairwise ~ targetword|Cond, adjust = "none")

#Plot 2 x 2. #RUN IF interaction is significant and/or main effect of target word is found.
emmip(mainresult, Cond~targetword, xlab = "Target Word", ylab = "Mean no. of thought intrusions", CIs = T) 

#RUN IF interaction is nonsignificant. Collapse across target word.
mainresult2<-aov_ez(id = "SubjID", dv = "finalDV.period2", data=RRR_Wegner87, 
                   between = c("Cond"))
summary(mainresult2)

```

### Multilevel model

Update: Oct 2022 (as requested by Editor)
The following codes is meant to retrieve the beta and standard error of the three-way interaction (Cond x Time pressure x Word Type), so that a subsequent multi-lab meta-analysis of this three-way interaction term (which requires the point estimate and the variance) can be computed.
Because the design has two within-subject factors (word type: target vs. nontarget words; time pressure: high vs. low), within a regression, this must be modeled as a MLM. 
Condition (supression vs. expression) is a between-subjects factor, hence this is not an issue.
See: https://stats.stackexchange.com/questions/396262/regression-within-and-between-subject-variable-interaction

```{r}

#Assuming we need DV from Periods 1 and 2:
m1 <- lmer(formula = intrusions ~ 1 + Cond * Period * Replication + (1 | SubjID), 
           data = data_long) #Random intercept of participants
summary(m1) 

#Assuming we need DV from Period 2 only:
data_long2<-data_long[!(data_long$Period=="1"),]

m1.mod <- lmer(formula = intrusions ~ 1 + Cond * Replication + (1 | Replication), 
               data = data_long2) #Random intercept of target words
summary(m1.mod) 

#From Wegner et al. (1987): "The mean of the summed thought measures during expression was 19.22, and this was significantly greater than the suppression mean of 6.78, F(l, 32) = 41.0 l, p < .0001"
#If F = 41, then t = 6.4. Note: df = 32. (n = 17 per group)
#Using formula for independent samples t-test, pooled SD = 5.667.
#Using formula for pooled SD, and assuming homogeneity of variance, standard deviation per group is SQRT(5.667) = 2.3806


#Alternatively, if one assumes that Replication (targetwords) is not a variable of interest, then RUNIF:
m2 <- lmer(formula = intrusions ~ 1 + Cond * Period + (1 | SubjID), 
           data = data_long) #Random intercept only. Note:  It is unlikely that a model with random intercept and random slope will converge, but we can try it: (1 + timepressure | ID) + (1 + wordtype | ID)
summary(m2) 

#RUNIF Replication is treated as a random effect (i.e., participants are nested within target word):
m3 <- lmer(formula = intrusions ~ 1 + Cond * Period * Replication + (1 | Replication:SubjID), 
           data = data_long) #Random intercept only. Note:  It is unlikely that a model with random intercept and random slope will converge, but we can try it: (1 + timepressure | ID) + (1 + wordtype | ID)
summary(m3) 

```

# Meta-analysis

The meta-analysis codes are for both Wegner et al. (1987) and Wegner & Erber (1992).

```{r}

#d1: Enhancement effect, contrast between concentration and suppression under low load
RRR_metaWE92.effectsize.d1 <- escalc(n2i = N.conc.low, n1i = N.supp.low, 
                                     m2i = M.conc.low, m1i = M.supp.low, 
                                     sd2i = SD.conc.low, sd1i = SD.supp.low, 
                                     data = RRR_metaWE92, 
                                     measure = "SMD", 
                                     append = TRUE) #Let op!  The effect size calculation is M1-M2, not M2-M1
overalld1 <- rma(yi, vi, data = RRR_metaWE92.effectsize.d1)
summary(overalld1) #These summary data will need to be saved manually in an Excel sheet, which the below forest plot codes will use.

#d2: Enhancement effect, contrast between concentration and suppression under high load
RRR_metaWE92.effectsize.d2 <- escalc(n2i = N.conc.high, n1i = N.supp.high, 
                                     m2i = M.conc.high, m1i = M.supp.high, 
                                     sd2i = SD.conc.high, sd1i = SD.supp.high, data = RRR_metaWE92, measure = "SMD", 
                                     append = TRUE) #Let op!  The effect size calculation is M1-M2, not M2-M1
overalld2 <- rma(yi, vi, data = RRR_metaWE92.effectsize.d2)
summary(overalld2) 

#d3: Rebound effect
RRR_metaWegner87.effectsize.d3 <- escalc(n2i = N.conc, n1i = N.supp, 
                                     m2i = M.conc, m1i = M.supp, 
                                     sd2i = SD.conc, sd1i = SD.supp, data = RRR_metaWegner87, measure = "SMD", 
                                     append = TRUE) #Let op!  The effect size calculation is M1-M2, not M2-M1
overalld3 <- rma(yi, vi, data = RRR_metaWegner87.effectsize.d3)
summary(overalld3) 

```

## Forest plot

Resources consulted:

- https://www.r-bloggers.com/2016/07/forest-plot-with-horizontal-bands/
- https://stackoverflow.com/questions/64595210/can-we-color-the-different-rows-covariates-studies-in-different-colors-in-r-fore

Note: The indentations made to the subgps command will not run well if you amend any of the subgps after running it once. To see the changes, you will have to reopen the data and start from beginning.

```{r}

subgps <- c(6,7,8,11,12,13,16,17,18,21,22,23,26,27,28,31,32,33, 36, 37, 38, 41, 42, 43) #OPTIONAL: RUN IF you want to indent d1, d2, d3 after the author's name.
data_meta_1$Lab[subgps] <- paste("  ",data_meta_1$Lab[subgps]) 

## The rest of the columns in the table. #OPTIONAL: RUN IF you want to indent d1, d2, d3 after the author's name.
tabletext <- cbind(c("Lab (Country)","\n",data_meta_1$Lab), 
                   c("N","\n",data_meta_1$N))

#OPTIONAL: RUN IF you want to indent d1, d2, d3 after the author's name.
styles <- fpShapesGp(
  lines = list(
    gpar(col = "black"), #Null
    gpar(col = "black"), #Null
    gpar(col = "green"), #Overall d1
    gpar(col = "green"),
    gpar(col = "green"),
    gpar(col = "black"), #Null
    gpar(col = "black"), #Null
    gpar(col = "black"),  #first d1
    gpar(col = "blue"),
    gpar(col = "red"),
    gpar(col = "white"), #Null
    gpar(col = "white"), #Null
    gpar(col = "black"), #second d1
    gpar(col = "blue"),
    gpar(col = "red"),
    gpar(col = "white"), #Null
    gpar(col = "white"), #Null
    gpar(col = "black"),
    gpar(col = "blue"),
    gpar(col = "red"),
    gpar(col = "white"), #Null
    gpar(col = "white"), #Null
    gpar(col = "black"),
    gpar(col = "blue"),
    gpar(col = "red"),
    gpar(col = "white"), #Null
    gpar(col = "white"), #Null
    gpar(col = "black"),
    gpar(col = "blue"),
    gpar(col = "red"),
    gpar(col = "white"), #Null
    gpar(col = "white"), #Null
    gpar(col = "black"),
    gpar(col = "blue"),
    gpar(col = "red"),
    gpar(col = "white"), #Null
    gpar(col = "white"), #Null
    gpar(col = "black"),
    gpar(col = "blue"),
    gpar(col = "red"),
    gpar(col = "white"), #Null
    gpar(col = "white"), #Null
    gpar(col = "black"),
    gpar(col = "blue"),
    gpar(col = "red")
  ),
  box = list(
    gpar(fill = "black"), #Null
    gpar(fill = "black"), #Null
    gpar(fill = "green"), #Overall d1
    gpar(fill = "green"),
    gpar(fill = "green"),
    gpar(fill = "black"), #Null
    gpar(fill = "black"), #Null
    gpar(fill = "black"),  #first d1
    gpar(fill = "blue"),
    gpar(fill = "red"),
    gpar(fill = "white"), #Null
    gpar(fill = "white"), #Null
    gpar(fill = "black"), #second d1
    gpar(fill = "blue"),
    gpar(fill = "red"),
    gpar(fill = "white"), #Null
    gpar(fill = "white"), #Null
    gpar(fill = "black"),
    gpar(fill = "blue"),
    gpar(fill = "red"),
    gpar(fill = "white"), #Null
    gpar(fill = "white"), #Null
    gpar(fill = "black"),
    gpar(fill = "blue"),
    gpar(fill = "red"),
    gpar(fill = "white"), #Null
    gpar(fill = "white"), #Null
    gpar(fill = "black"),
    gpar(fill = "blue"),
    gpar(fill = "red"),
    gpar(fill = "white"), #Null
    gpar(fill = "white"), #Null
    gpar(fill = "black"),
    gpar(fill = "blue"),
    gpar(fill = "red"),
    gpar(fill = "white"), #Null
    gpar(fill = "white"), #Null
    gpar(fill = "black"),
    gpar(fill = "blue"),
    gpar(fill = "red"),
    gpar(fill = "white"), #Null
    gpar(fill = "white"), #Null
    gpar(fill = "black"),
    gpar(fill = "blue"),
    gpar(fill = "red")
  ) 
)

forestplot(labeltext=tabletext, 
           graph.pos=3, 
           mean=c(NA,NA,data_meta_1$Point), 
           lower=c(NA,NA,data_meta_1$Low),
           upper=c(NA,NA,data_meta_1$High),
           txt_gp=fpTxtGp(label=gpar(cex=1.25),
                          ticks=gpar(cex=1.1),
                          xlab=gpar(cex = 1.2),
                          title=gpar(cex = 1.2)),
           shapes_gp = styles,
           zero=0, cex=0.9, 
           lineheight = unit(5, "mm"), 
           boxsize=0.5, 
           colgap=unit(6,"mm"),
           lwd.ci=2, 
           ci.vertices=TRUE, 
           ci.vertices.height = 0.4)

```

# NEW: JUNE 2022

Below is for d1 and d2 (immediate enhancement effect under high and low time pressure, respectively)


###INTENTION: SPLIT d1 and d2 from d3, as requested by Editor###

```{r}

subgps <- c(6,7,11,12,16,17,21,22,26,27,31,32) #this is optional; this only needs to be tweaked if you want the d1 and d2 to be indented. If not, there is no need to run this code.
data_meta_2$Lab[subgps] <- paste("  ",data_meta_2$Lab[subgps]) #this is optional; if d1 and d2 doesn't need to be indented, then no need to run this.

## The rest of the columns in the table. 
tabletext <- cbind(c("Lab (Country)","\n",data_meta_2$Lab), 
                   c("N","\n",data_meta_2$N)) #\n means new line


styles <- fpShapesGp(
  lines = list(
    gpar(col = "black"), #Null
    gpar(col = "black"), #Null
    gpar(col = "green"), #Overall d1
    gpar(col = "green"), #Overall d2
    gpar(col = "black"), #Null
    gpar(col = "black"), 
    gpar(col = "black"), #first d1 
    gpar(col = "blue"),  #first d2
    gpar(col = "white"), #Null
    gpar(col = "white"), #Null
    gpar(col = "black"), #second d1
    gpar(col = "blue"),  #second d2
    gpar(col = "white"), #Null
    gpar(col = "white"), #Null
    gpar(col = "black"), #third d1
    gpar(col = "blue"),  #third d2
    gpar(col = "white"), #Null
    gpar(col = "white"), #Null
    gpar(col = "black"),
    gpar(col = "blue"),
    gpar(col = "white"), #Null
    gpar(col = "white"), #Null
    gpar(col = "black"),
    gpar(col = "blue"),
    gpar(col = "white"), #Null
    gpar(col = "white"), #Null
    gpar(col = "black"),
    gpar(col = "blue"),
    gpar(col = "white"), #Null
    gpar(col = "white"), #Null
    gpar(col = "black"),
    gpar(col = "blue"),
    gpar(col = "white"), #Null
    gpar(col = "white"), #Null
    gpar(col = "black"),
    gpar(col = "blue")
  ),
  box = list(
    gpar(fill = "black"), #Null
    gpar(fill = "black"), #Null
    gpar(fill = "green"), #Overall d1
    gpar(fill = "green"),
    gpar(fill = "black"), #Null
    gpar(fill = "black"), #Null
    gpar(fill = "black"),  #first d1
    gpar(fill = "blue"),
    gpar(fill = "white"), #Null
    gpar(fill = "white"), #Null
    gpar(fill = "black"), #second d1
    gpar(fill = "blue"),
    gpar(fill = "white"), #Null
    gpar(fill = "white"), #Null
    gpar(fill = "black"),
    gpar(fill = "blue"),
    gpar(fill = "white"), #Null
    gpar(fill = "white"), #Null
    gpar(fill = "black"),
    gpar(fill = "blue"),
    gpar(fill = "white"), #Null
    gpar(fill = "white"), #Null
    gpar(fill = "black"),
    gpar(fill = "blue"),
    gpar(fill = "white"), #Null
    gpar(fill = "white"), #Null
    gpar(fill = "black"),
    gpar(fill = "blue"),
    gpar(fill = "white"), #Null
    gpar(fill = "white"), #Null
    gpar(fill = "black"),
    gpar(fill = "blue"),
    gpar(fill = "white"), #Null
    gpar(fill = "white"), #Null
    gpar(fill = "black"),
    gpar(fill = "blue")
  ) 
)

forestplot(labeltext=tabletext, graph.pos=3, 
           mean=c(NA,NA,data_meta_2$Point), 
           lower=c(NA,NA,data_meta_2$Low), upper=c(NA,NA,data_meta_2$High),
           txt_gp=fpTxtGp(label=gpar(cex=1.25),
                          ticks=gpar(cex=1.1),
                          xlab=gpar(cex = 1.2),
                          title=gpar(cex = 1.2)),
           shapes_gp = styles,
           zero=0, cex=0.9, lineheight = unit(5, "mm"), boxsize=0.5, colgap=unit(6,"mm"),
           lwd.ci=2, ci.vertices=TRUE, ci.vertices.height = 0.4)

#note: If plot is too big for screen, save it as pdf then screenshot to Word.


```


```{r}

#The forest plot below is only for d3 (rebound effect), as requested by Editor.
library(readxl)
library(forestplot)

data <- read_excel("RRR_Hyperaccesibility.xlsx", sheet = "forestplotd3") #note new sheet name
View(data)

## The rest of the columns in the table. 
tabletext <- cbind(c("Lab (Country)","\n",data$Lab), 
                   c("N","\n",data$N)) #\n means new line

forestplot(labeltext=tabletext, graph.pos=3, 
           mean=c(NA,NA,data$Point), 
           lower=c(NA,NA,data$Low), upper=c(NA,NA,data$High),
           zero=0, cex=0.9, lineheight = unit(5, "mm"), boxsize=0.5, colgap=unit(6,"mm"),
           lwd.ci=2, ci.vertices=TRUE, ci.vertices.height = 0.4)

#Updated: Oct 2022 (as requested by Editor)
  #Editor requested a meta-analysis of the three-way interaction between Condition, Time Pressure, and Word Type.

#3-way interaction (Condition x Time Pressure x Word Type)
library(meta) 
summary(intWE92) <- metagen(TE= threeway.beta.int_term, seTE = threeway.SE.int_term, data = RRR_metaWE92)
summary(intWegner87) <- metagen(TE= threeway.beta.int_term, seTE = threeway.SE.int_term, data = RRR_metaWegner87)


```


